Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-02-19 Writing/CEA_2nd_round/replies_rev_2.rmd

# Comments:

@@

<span style="color:blue"> 
The extra "some" was removed from the sentence.
</span>

@@

<span style="color:blue"> 
The typo was corrected. 
</span>

@@

<span style="color:blue">  
The grammatical error was corrected. 
</span>

@@

<span style="color:blue">  
We removed "much" from the sentence.
</span>

>>>>

Thank you so much for your comments. By addressing them, we believe the manuscript is improved significantly. Below you will find your comments in bold and our replies in a regular font.

<br>

@@

<span style="color:blue"> 
The extra "some" was removed from the sentence (see p15 l.249).
</span>

@@

<span style="color:blue"> 
The typo was corrected (see p19 l.320). 
</span>

@@

<span style="color:blue">  
The grammatical error was corrected (see p20 l.340). 
</span>

@@

<span style="color:blue">  
We removed "much" from the sentence (see p24 l.366).
</span>

### 2022-02-19 Writing/appendix.rmd

Figure A.1 shows an example of CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with apparent electrical conductivity ($\textit{ecs}$)($dS/m$) and topographical $\textit{slope}$ ($degree$) as variables to explain the heterogeneity of the impact of the treatment impact.

>>>>

Figure A.1 shows an example of CT where the treatment is an increase in seed rate from $27,000$ seeds/ha (control) to $31,000$ seeds/ha (treated) with apparent electrical conductivity ($\textit{ecs}$) ($dS/m$) and topographical $\textit{slope}$ ($degree$) as variables to explain the heterogeneity of the impact of the treatment impact.
